Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-06 CVPR16/Source/experiments2.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D localization in road scenes. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

\subsection{Association Experiments}
%\vspace{-0.2cm}
\paragraph{Setup}
We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

\begin{figure*}[!!t]
\centering
%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
  \vspace{-0.3cm}
  \caption{\small Association errors on different sets of input point tracks. Numbers on y-axis represent data sequence numbers in KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
  \vspace{-0.3cm}
  \label{fig:assoc-occ-results}
\end{figure*}

\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{\small Mean association errors on different sets of input point tracks over all sequences of KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{table}

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.090\textwidth}
\begin{figure*}[!!t]
  \centering
  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
    & Associations & Association Error & Associations & Association Error\\
    \rotatebox{90}{\hspace{1em} BBox}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} BM}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} RAS}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} Ours}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \vspace{-0.3cm}
  \caption{\small Qualitative results of the association experiment. The odd columns
  show the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. The even columns show the
probabilistic error in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0-1 error.}
\label{fig:qualitative}
\vspace{-0.3cm}
\end{figure*}

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

\vspace{-0.4cm}
\paragraph{Results}
Figure~\ref{fig:assoc-occ-results} shows the association errors -- the percentages of point tracks incorrectly assigned to objects -- for all methods on the four sets of input point tracks, for each sequence of the KITTI dataset. The mean results over all sequences are summarized in Table~\ref{tab:meanAssoc}. From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean error on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, thus, the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.

@@

\begin{table}
  \begin{tabular}{lrr}
    \toprule
    Energy & t & dim \\
    \midrule
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05  & {\bf 1.59}\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & {\bf 3.24}  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
  \label{tab:localizationExperiment}
\end{table}

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies.  The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. We observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

>>>>

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D object localization in road scenes. For our experiments, we use 35 sequences of the KITTI raw dataset~\cite{Geiger_etal_2012}, which are recorded under a variety of driving conditions and include 10,088 frames and 634 object tracks in total. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

\subsection{Association Experiments}
%\vspace{-0.2cm}
\paragraph{Setup}
We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinities (BM)~\cite{Brox_Malik_2010}.

\begin{figure*}[!!t]
\centering
%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
  \vspace{-0.3cm}
  \caption{\small Association errors on different sets of input point tracks. Numbers on x-axis represent sequence numbers in the KITTI raw dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
  \vspace{-0.3cm}
  \label{fig:assoc-occ-results}
\end{figure*}

\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  Point tracks & Ours & BBox & BM & RAS\\
  \midrule
  Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
  Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
  All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{\small Mean association errors on different sets of input point tracks over all sequences. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{table}

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.090\textwidth}
\begin{figure*}[!!t]
  \centering
  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
    & Associations & Errors & Associations & Errors\\
    \rotatebox{90}{\hspace{1em} BBox}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} BM}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} RAS}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} Ours}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \vspace{-0.3cm}
  \caption{\small Qualitative results of the association experiment. The ``Associations" columns
  show the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. The ``Errors" columns show the
probabilistic errors in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0 and 1 errors.}
\label{fig:qualitative}
\vspace{-0.3cm}
\end{figure*}

@@

For each sequence, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters (position, orientation, and dimensions) of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

\vspace{-0.4cm}
\paragraph{Results}
Figure~\ref{fig:assoc-occ-results} shows the association errors -- the percentages of point tracks incorrectly assigned to objects -- for all methods on the four sets of input point tracks, for each sequence. The mean results over all sequences are summarized in Table~\ref{tab:meanAssoc}. From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean error on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, thus, the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.

@@

\begin{table}
  \begin{tabular}{lrr}
    \toprule
    Method & t & dim \\
    \midrule
    Point cloud fitting
    & 6.87 & 4.02\\
    Initialization
    & 5.61 & 3.23\\
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05  & {\bf 1.59}\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & {\bf 3.24}  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
  \label{tab:localizationExperiment}
\end{table}

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies against the initialization by~\cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, e.g., only the back of a car is visible, we rely on 3D size priors). The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion.

From Table~\ref{tab:localizationExperiment}, the baseline method has the highest errors, which is likely due to lack of point tracks and incorrect point-to-object associations (using detection bounding boxes). Moreover, minimizing different combinations of energies yields lower errors than the initialization by~\cite{Song_Chandraker_2014}, which shows the advantage of our energy minimization. Finally, we observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

%We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies with two baselines. We initialize the unknowns using \cite{Song_Chandraker_2014} whose accuracy is reported as \emph{Initialization} in the table. We develop a simple baseline by fitting cuboids to the point cloud created by triangulation of point tracks in two successive frames. The accuracy of this baseline is reported as \emph{Point cloud fit} in the table. The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. We observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

### 2016-04-06 CVPR16/Source/intro.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate the application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.

In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}. But motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.

>>>>

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusions are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate the application of our formulations for road scenes from the KITTI raw dataset \cite{Geiger_etal_2012}.

In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}. However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.
